---
title: "econ401 final project R Notebook"
output: html_notebook
---

Libraries:
```{r libraries, results = "markup"}
library(tidyverse)
library(readr)
library(rvest)
library(stats)
library(readxl)
library(dplyr)
library(stringr)
library(ggplot2)
library(ggthemes)
library(stringr)
library(data.table)
library(geojsonio)
library(leaflet)
library(rgdal)
library(haven)
library(stargazer)
library(RColorBrewer)
```

Data:
```{r data, include = FALSE}
# GDP up to Feb 2020
# https://ihsmarkit.com/products/us-monthly-gdp-index.html
gdp.index.data <- readxl::read_xlsx('US-Monthly-GDP-History-Data.xlsx', sheet = 3)
gdp.index <- gdp.index.data
colnames(gdp.index)[1] <- "Y_M"
year.month <- str_split_fixed(gdp.index$Y_M, ' - ', 2)
colnames(year.month) <- c('Year', 'Month')
gdp.index <- cbind(year.month, gdp.index[, -1])
gdp.annual <- gdp.index %>%
  group_by(Year) %>%
  summarize(MaxGDP = max(`Monthly Real GDP Index`),
            MinGDP = min(`Monthly Real GDP Index`))

# https://nces.ed.gov/programs/digest/d18/tables/dt18_306.10.asp
enrollment.data <- read_xls('tabn306.10.xls')
enrollment <- enrollment.data[1:12]
# enrollment is in thousands
enrollment <- enrollment[-c(1, 3, 15, 27, 39, 51, 63, 75, 99, 111, 123, 135:139), ]
col1 <- data.frame(str_remove_all(enrollment[[1]], '\\.'), stringsAsFactors = FALSE)
col1[2, 1] <- "All_Students"
enrollment <- cbind(col1, enrollment[, -1])
enrollment <- t(enrollment)
rownames(enrollment) <- c()
colnames(enrollment) <- enrollment[1, ]
enrollment <- data.frame(enrollment)
colnames(enrollment)[1] <- 'Year'
enrollment <- enrollment[-1, ]
Years <- as.numeric(str_extract(enrollment$Year, "[:digit:]{4}"))
enrollment <- cbind(Years, enrollment[, -1])
enrollment <- data.frame(lapply(enrollment, function(x){ 
  gsub("---", NA, x)
}))
str(enrollment)

enrollment1 <- enrollment[, 1:2]
gdp.annual1 <- gdp.annual
all.students <- as.numeric(enrollment[4:11, 2])

gdp.annual$Year <- as.factor(gdp.annual$Year)
enrollment1$Years <- as.factor(enrollment1$Years)
enrollment1$All_Students <- as.numeric(as.character(enrollment1$All_Students))
```

Model 3:

  First making a graph of annual GDP highs and lows -- maybe a temporary proxy for recessions?
```{r graph1, include = FALSE}
gdp.annual %>%
  ggplot() +
  geom_line(mapping = aes(x = Year,
                 y = MaxGDP,
                 group = 1)) +
  geom_line(mapping = aes(x = Year,
                          y = MinGDP,
                          group = 1)) +
  theme_economist() +
  ylab('Real GDP')
```

  Annual enrollment graph:
```{r graph2, include = FALSE}
enrollment1 %>%
  ggplot() +
  geom_line(mapping = aes(x = Years,
                          y = All_Students,
                          group = 1)) +
  theme_economist() +
  ylab('Enrollment')
```

  Join enrollment data and gdp data to create linear model test:
```{r lm1, include = FALSE}
test <- inner_join(enrollment1, gdp.annual1,
          by = c("Years" = "Year"))

lm1 <- lm(All_Students ~ MaxGDP,
          data = test,
          na.action = na.omit)
summary(lm1)
```

  Graph it?
```{r graph3_4, include = FALSE}
test %>%
  ggplot() +
  geom_line(aes(x = Years,
                 y = All_Students,
                group = 1)) +
  theme_economist() +
  ylab('Enrollment by All Students')

test %>%
  ggplot() +
  geom_line(aes(x = Years,
                 y = MaxGDP,
                 group = 1)) +
  # geom_abline(slope = 0.8015, intercept = 6316.7207) +
  theme_economist()
```

College Proximity Question 5/3:
(Reading in Ivy's data)
```{r read proximity data, results = "markup"}
# cz_college <- read_dta("cz_college.dta")
cz <- read_dta('cz.dta')
# colleges <- read_dta('colleges.dta')
# mobility.results <- read_xlsx('mobility_results.xlsx')
```

Read in/create mobility data:
(Trends in Mobility: Commuting Zone Intergenerational Mobility Estimates by Birth Cohort)
https://opportunityinsights.org/data/?geographic_level=101&topic=0&paper_id=0#resource-listing
```{r mobility data, include=FALSE}
# mobility.data <- read_xls('onlinedata1_trends.xls')
# colnames(mobility.data) <- mobility.data[15, ]
# mobility <- mobility.data[-c(1:16), ]
# mobility.1986 <- mobility %>%
#   filter(`Birth Cohort` == 1986)
# mobility.1986$`Commuting Zone` <- as.numeric(mobility.1986$`Commuting Zone`)
# cz.mobility.data <- full_join(mobility.1986[, c(1, 3:8)],
#                   cz,
#                   by = c(`Commuting Zone` = 'cz'))
# 
# cz.mobility <- cz.mobility.data[, c(1:8, 2132:2137)]
# cz.mobility <- cz.mobility[, c(1, 8, 9:14, 3:7, 2)]
# write_csv(cz.mobility, 'cz.mobility.csv')
cz.mobility <- read_csv('cz.mobility.csv')
```

Read in geojson file:
```{r geojson}
cz.geojson <- geojson_read("cz1990.json",
                        what = "sp")
# View(cz.geojson@data)
# cz.geojson %>%
#   leaflet() %>%
#   #addTiles() %>%
#   addPolygons() %>%
#   setView(-96, 37.8, 3)
```

Commuting zones on the map (cz.geojson@data) are in 1990s format. They need to be converted so our post-2000 data can be connected to the shapefiles:
(https://www.ers.usda.gov/data-products/commuting-zones-and-labor-market-areas/)
```{r cz shape combine, include = FALSE}
# cz.conversions <- read_xls('cz00_eqv_v1.xls')
# cz.conversions <- cz.conversions[, c(2:4)]
# cz.conversions$`Commuting Zone ID, 1990` <- as.numeric(cz.conversions$`Commuting Zone ID, 1990`)
# cz.conversions$`Commuting Zone ID, 1980` <- as.numeric(cz.conversions$`Commuting Zone ID, 1980`)
# colnames(cz.conversions)[2] <- 'cz1990'
# colnames(cz.conversions)[1] <- 'cz2000'
# colnames(cz.conversions)[3] <- 'cz1980'
# 
# head(cz.geojson@data)
# cz.geo <- cz.geojson
# colnames(cz.mobility)[1] <- 'cz1990'
# 
# cz.geo@data <- full_join(cz.geo@data,
#                   cz.conversions[, -3],
#                   by = c('cz' = 'cz1990'))
# cz.geo@data <- left_join(cz.geo@data,
#                          cz.mobility,
#                          by = c('cz' = 'cz1990'))
# 
# cz.geo %>%
#   leaflet() %>%
#   addPolygons() %>%
#   setView(-96, 37.8, 3)

# geojson_write(cz.geo,
#               file = "cz_geo.geojson",
#               overwrite = TRUE)

cz.geo <- geojson_read("cz_geo.geojson",
                        what = "sp")
```

Making the map actually display data:
```{r}
bins1 <- c(1, 5, 10, 20, 40, 60, 90)
        
colors1 <- colorBin(bins = bins1,
                    palette = "YlOrRd",
                    domain = cz.geo@data$ncollege)
        
cz.geo %>%
  leaflet() %>%
  addTiles() %>%
  addPolygons(fillColor = ~colors1(cz.geo@data$ncollege),
              weight = 1,
              color = "white",
              opacity = 0.5,
              fillOpacity = .7) %>%
  setView(-96, 37.8, 3) %>%
  addLegend(pal = colors1,
            values = cz.geo@data$ncollege,
            title = "Number of Colleges in Commuting Zone")


```


Try to run some lms:

  Ivy's STATA code:

    foreach x of varlist ncollege nfouryr nfouryrpriv npub nelite hascollege{
    	
    foreach y of varlist kfr_pooled_pooled_p1 kfr_pooled_pooled_p25 kfr_pooled_pooled_p50 kfr_pooled_pooled_p75 kfr_pooled_pooled_p100 {
    	reg `y' `x' popdensity2010 med_hhinc2016, r 
    	outreg2 using `x'_kfr, excel append ctitle(`y')
    }
    
  Variables of interest:
  
```{r}
yvar1 <- "kfr_pooled_pooled_p1"
xvars1 <- c("ncollege", "nfouryr", "nfouryrpriv", "npub", "nelite", "hascollege", "popdensity2010", "med_hhinc2016")
cz1 <- cz[, c(yvar1, xvars1)]

lm.model1 <- as.formula(paste0(yvar1, " ~ ", paste0(xvars1, collapse =  " + ")))

```

testing?
```{r}
lm.kfr_p1 <- lm(lm.model1,
                data = cz)
summary(lm.kfr_p1)

stargazer(cz1, type = "text", title="Descriptive statistics", digits=1, out="table1.txt")

stargazer(lm.kfr_p1,
          type = "text",
          dep.var.labels = c("kfr_pooled_pooled_p1"))
 #          ,
 #          covariate.labels = c("Gross horsepower", "Rear axle ratio","Four foward gears",
 # "Five forward gears","Type of transmission (manual=1)"), out="models.txt")


```

nelite on kfr at different levels
```{r}
yvar.p1 <- "kfr_pooled_pooled_p1"
yvar.p25 <- "kfr_pooled_pooled_p25"
yvar.p50 <- "kfr_pooled_pooled_p50"
yvar.p75 <- "kfr_pooled_pooled_p75"
yvar.p100 <- "kfr_pooled_pooled_p100"
xvars.nelite <- c("nelite", "popdensity2010", "med_hhinc2016")
lm.nelite.p1 <- as.formula(paste0(yvar.p1, " ~ ", paste0(xvars.nelite, collapse =  " + ")))
lm.nelite.p25 <- as.formula(paste0(yvar.p25, " ~ ", paste0(xvars.nelite, collapse =  " + ")))
lm.nelite.p50 <- as.formula(paste0(yvar.p50, " ~ ", paste0(xvars.nelite, collapse =  " + ")))
lm.nelite.p75 <- as.formula(paste0(yvar.p75, " ~ ", paste0(xvars.nelite, collapse =  " + ")))
lm.nelite.p100 <- as.formula(paste0(yvar.p100, " ~ ", paste0(xvars.nelite, collapse =  " + ")))
nelite.p1 <- lm(lm.nelite.p1, cz)
nelite.p25 <- lm(lm.nelite.p25, cz)
nelite.p50 <- lm(lm.nelite.p50, cz)
nelite.p75 <- lm(lm.nelite.p75, cz)
nelite.p100 <- lm(lm.nelite.p100, cz)
txttable.nelite <- stargazer(nelite.p1, nelite.p25, nelite.p50, nelite.p75, nelite.p100,
          type = "text",
          title = "The Effect of Elite Colleges in Commuting Zone on the Probability that a Child from the 20th Percentile Falls in Each Income Percentile as an Adult",
          dep.var.caption = "Parent Income Percentile",
          dep.var.labels = c("Bottom 1%", "25%", "50%", "75%", "Top 1%"),
          # notes = "Where nelite is the number of elite colleges in commuting zone (cz), popdensity2010 is the cz's popultion density, and med_hhinc2016 is the median household income in cz in 2016.",
          # notes.append = TRUE,
          # notes.align = "l",
          out = "nelitetable.txt")
htmtable.nelite <- stargazer(nelite.p1, nelite.p25, nelite.p50, nelite.p75, nelite.p100,
          type = "html",
          dep.var.labels = c("Bottom 1%", "25%", "50%", "75%", "Top 1%"),
          out = "nelitetable.html")
summary(lm.nelite.p1)
```
image print cheeeeck:
```{r}
tables <- data.frame(tablename = c("hascollege_black",
                                "hascollege_kfr",
                                "hascollege_top20",
                                "hascollege_white",
                                "ncollege_black",
                                "ncollege_kfr",
                                "ncollege_top20",
                                "ncollege_white",
                                "nelite_black",
                                "nelite_kfr",
                                "nelite_top20",
                                "nelite_white",
                                "nfouryr_black",
                                "nfouryr_kfr",
                                "nfouryr_top20",
                                "nfouryr_white",
                                "nfouryrpriv_black",
                                "nfouryrpriv_kfr",
                                "nfouryrpriv_top20",
                                "nfouryrpriv_white",
                                "npub_black",
                                "npub_kfr",
                                "npub_top20",
                                "npub_white",
                                "sumstats"),
                     picture = c("C:\\\\Users\\neris\\OneDrive - Middlebury College\\Last Semester\\ECON Inequality & Justice\\econ0401\\hascollege_black.png",
                                 "C:\\Users\\neris\\OneDrive - Middlebury College\\Last Semester\\ECON Inequality & Justice\\econ0401\\hascollege_kfr.png",
                                 "C:\\Users\\neris\\OneDrive - Middlebury College\\Last Semester\\ECON Inequality & Justice\\econ0401\\hascollege_top20.png",
                                 "C:\\Users\\neris\\OneDrive - Middlebury College\\Last Semester\\ECON Inequality & Justice\\econ0401\\hascollege_white.png",
                                 "C:\\Users\\neris\\OneDrive - Middlebury College\\Last Semester\\ECON Inequality & Justice\\econ0401\\ncollege_black.png",
                                 "C:\\Users\\neris\\OneDrive - Middlebury College\\Last Semester\\ECON Inequality & Justice\\econ0401\\ncollege_kfr.png",
                                 "C:\\Users\\neris\\OneDrive - Middlebury College\\Last Semester\\ECON Inequality & Justice\\econ0401\\ncollege_top20.png",
                                 "C:\\Users\\neris\\OneDrive - Middlebury College\\Last Semester\\ECON Inequality & Justice\\econ0401\\ncollege_white.png",
                                 "C:\\Users\\neris\\OneDrive - Middlebury College\\Last Semester\\ECON Inequality & Justice\\econ0401\\nelite_black.png",
                                 "C:\\Users\\neris\\OneDrive - Middlebury College\\Last Semester\\ECON Inequality & Justice\\econ0401\\nelite_kfr.png",
                                 "C:\\Users\\neris\\OneDrive - Middlebury College\\Last Semester\\ECON Inequality & Justice\\econ0401\\nelite_top20.png",
                                 "C:\\Users\\neris\\OneDrive - Middlebury College\\Last Semester\\ECON Inequality & Justice\\econ0401\\nelite_white.png",
                                 "C:\\Users\\neris\\OneDrive - Middlebury College\\Last Semester\\ECON Inequality & Justice\\econ0401\\nfouryr_black.png",
                                 "C:\\Users\\neris\\OneDrive - Middlebury College\\Last Semester\\ECON Inequality & Justice\\econ0401\\nfouryr_kfr.png",
                                 "C:\\Users\\neris\\OneDrive - Middlebury College\\Last Semester\\ECON Inequality & Justice\\econ0401\\nfouryr_top20.png",
                                 "C:\\Users\\neris\\OneDrive - Middlebury College\\Last Semester\\ECON Inequality & Justice\\econ0401\\nfouryr_white.png",
                                 "C:\\Users\\neris\\OneDrive - Middlebury College\\Last Semester\\ECON Inequality & Justice\\econ0401\\nfouryrpriv_black.png",
                                 "C:\\Users\\neris\\OneDrive - Middlebury College\\Last Semester\\ECON Inequality & Justice\\econ0401\\nfouryrpriv_kfr.png",
                                 "C:\\Users\\neris\\OneDrive - Middlebury College\\Last Semester\\ECON Inequality & Justice\\econ0401\\nfouryrpriv_top20.png",
                                 "C:\\Users\\neris\\OneDrive - Middlebury College\\Last Semester\\ECON Inequality & Justice\\econ0401\\nfouryrpriv_white.png",
                                 "C:\\Users\\neris\\OneDrive - Middlebury College\\Last Semester\\ECON Inequality & Justice\\econ0401\\npub_black.png",
                                 "C:\\Users\\neris\\OneDrive - Middlebury College\\Last Semester\\ECON Inequality & Justice\\econ0401\\npub_kfr.png",
                                 "C:\\Users\\neris\\OneDrive - Middlebury College\\Last Semester\\ECON Inequality & Justice\\econ0401\\npub_top20.png",
                                 "C:\\Users\\neris\\OneDrive - Middlebury College\\Last Semester\\ECON Inequality & Justice\\econ0401\\npub_white.png",
                                 "C:\\Users\\neris\\OneDrive - Middlebury College\\Last Semester\\ECON Inequality & Justice\\econ0401\\sumstats.png"))
tables$tablename <- as.character(tables$tablename)
tables$picture <- as.character(tables$picture)

# write_csv(tables, "outputtables.csv")

# tables %>%
#   ggplot() +
#   geom_bar(stat = "identity") +
#   geom_image(aes(image = picture),
#              size = .2)
```


Plotting the lms:

```{r}
lm1 <- lm(kfr_pooled_pooled_mean ~ ncollege + popdensity2010 + med_hhinc2016,
   data = cz)
ncollege.seq <- seq(from = 0, to = 82, by = 5)
kfr_pooled_pooled_mean.seq <- seq(from = 0.2490857, to = 0.6728090, by = .025)
popdensity2010.seq <- seq(from = 0.106, to = 5635.804, by = 300)
med_hhinc2016.seq <- seq(from = 26645, to = 103043, by = 3750)
grid1 <- expand.grid('ncollege' = ncollege.seq,
                     'kfr_pooled_pooled_mean' = kfr_pooled_pooled_mean.seq,
                     'popdensity2010'  = popdensity2010.seq,
                     'med_hhinc2016' = med_hhinc2016.seq)
predictions <- predict.lm(lm1,
                          grid1)
final.data <- data.frame(grid1, predictions)

final.data %>%
  ggplot(aes(x = ncollege,
             y = predictions)) +
  geom_line() +
  stat_smooth(aes(x = ncollege, y = predictions), method = "lm",
              formula = y ~ kfr_pooled_pooled_mean ~ ncollege + popdensity2010 + med_hhinc2016, se = FALSE) +
  theme_economist() +
  scale_color_brewer(palette = "YlOrRd")

ggplot(aes(x = plotx, y = ploty)) %>%
  geom_abline()

lm2 <- lm(kfr_black_pooled_p50 ~ ncollege + popdensity2010 + med_hhinc2016,
   data = cz)
lm3 <- lm(kfr_white_pooled_p50 ~ ncollege + popdensity2010 + med_hhinc2016,
   data = cz)

cz %>%
  ggplot(aes(x = ncollege, y = kfr_pooled_pooled_mean)) +
  geom_abline(intercept = 3.799e-01, slope = -8.572e-04) +
  geom_abline(intercept = 3.523e-01, slope = -9.573e-04) +
  geom_abline(intercept = 4.973e-01, slope = -9.133e-04) +
  ylim(3.5e-01, 0.5)

plot(lm1)

```



Wait lemme try the long format thing:

```{r}
kfr.cols <- c("kfr_black_pooled_p1", "kfr_black_pooled_p25", "kfr_black_pooled_p50", "kfr_black_pooled_p75", "kfr_black_pooled_p100", "kfr_pooled_pooled_p1", "kfr_pooled_pooled_p25", "kfr_pooled_pooled_p50", "kfr_pooled_pooled_p75", "kfr_pooled_pooled_p100", "kfr_white_pooled_p1", "kfr_white_pooled_p25", "kfr_white_pooled_p50", "kfr_white_pooled_p75", "kfr_white_pooled_p100")

kfr.test <- cz[, c(kfr.cols, "ncollege", "nfouryr", "nelite", "npub", "popdensity2010", "med_hhinc2016")]

keycol1 <- "category"
valuecol1 <- "kfr"
gathercols1 <- kfr.cols

data_long <- gather_(kfr.test, keycol1, valuecol1, gathercols1)

data_longa <- data_long %>%
  filter(str_detect(data_long$category, "black", negate = FALSE)) %>%
  mutate(race = "black")

data_longa$category <- data_longa$category %>%
  str_replace_all("kfr_black_pooled_p1", "1") %>%
  str_replace_all("kfr_black_pooled_p25", "25") %>%
  str_replace_all("kfr_black_pooled_p50", "50") %>%
  str_replace_all("kfr_black_pooled_p75", "75") %>%
  str_replace_all("kfr_black_pooled_p100", "100")

data_longb <- data_long %>%
  filter(str_detect(data_long$category, "white", negate = FALSE)) %>%
  mutate(race = "white")

data_longb$category <- data_longb$category %>%
  str_replace_all("kfr_white_pooled_p1", "1") %>%
  str_replace_all("kfr_white_pooled_p25", "25") %>%
  str_replace_all("kfr_white_pooled_p50", "50") %>%
  str_replace_all("kfr_white_pooled_p75", "75") %>%
  str_replace_all("kfr_white_pooled_p100", "100")

data_longc <- data_long %>%
  filter(str_detect(data_long$category, "pooled_pooled", negate = FALSE)) %>%
  mutate(race = "pooled")

data_longc$category <- data_longc$category %>%
  str_replace_all("kfr_pooled_pooled_p1", "1") %>%
  str_replace_all("kfr_pooled_pooled_p25", "25") %>%
  str_replace_all("kfr_pooled_pooled_p50", "50") %>%
  str_replace_all("kfr_pooled_pooled_p75", "75") %>%
  str_replace_all("kfr_pooled_pooled_p100", "100")

long.data1 <- rbind(data_longa, data_longb,
                    data_longc) 

long.data1a <- long.data1 %>%
  mutate(black = ifelse(race == "black",
                        TRUE,
                        FALSE),
         white = ifelse(race == "white",
                        TRUE,
                        FALSE))

long.lm1 <- lm(kfr ~ ncollege + black + white + popdensity2010 + med_hhinc2016,
   data = long.data1a)
summary(long.lm1)

# write_csv(long.data1a, "long_kfr.csv")
# long.data1a <- read_csv('long_kfr.csv')

```

Output table:
```{r}
stargazer(long.lm1,
          type = "text")
```

Try with interaction & w/o hhinc:
```{r}
long.lm1.wohhinc <- lm(kfr ~ ncollege + black + white + popdensity2010,
   data = long.data1a)
long.lm1a <- lm(kfr ~ ncollege + black + white + black*ncollege + white*ncollege + popdensity2010 + med_hhinc2016,
   data = long.data1a)
summary(long.lm1a)
```
No significant difference. Will stick to original model.

Visualize it maybe?:
```{r}
long.lm1.race <- lm(kfr ~ ncollege + race + popdensity2010 + med_hhinc2016,
   data = long.data1a)

ncollege.seq <- seq(from = 0, to = 82, by = 1)
race.seq <- unique(long.data1a$race)
popdensity2010.seq <- seq(from = 0.106, to = 5635.804, by = 300)
med_hhinc2016.seq <- seq(from = 26645, to = 103043, by = 3750)
grid1 <- expand.grid('ncollege' = ncollege.seq,
                     'race' = race.seq,
                     'popdensity2010'  = popdensity2010.seq,
                     'med_hhinc2016' = med_hhinc2016.seq)
predictions <- predict.lm(long.lm1.race,
                          grid1)
final.data <- data.frame(grid1, predictions)


final.data %>%
  group_by(race, ncollege) %>% 
  summarise(meanpredict = mean(predictions)) %>%
  ggplot(aes(x = ncollege,
             y = meanpredict)) +
  geom_line(aes(color = factor(race)),
            size = 1.5) +
  theme_economist() +
  theme(plot.title = element_text(hjust = 0, size = 10, face = "bold")) +
  scale_color_brewer(palette = "YlOrRd") +
  ylab("Household Income Percentile Rank") +
  ggtitle("Effect of Number of Colleges in CZ on Household Income Percentile Rank by Race") + 
  labs(color = "")


```

Making new image table:
```{r}
outputtables <- data.frame(tablename = c("Black Child Income Outcomes",
                                   "White Child Income Outcomes",
                                   "All Child Income Outcomes",
                                   "All Child Probability of Reaching Top 20%"),
                     path = c("C:\\Users\\neris\\OneDrive - Middlebury College\\Last Semester\\ECON Inequality & Justice\\econ0401\\black_combined.png",
                              "C:\\Users\\neris\\OneDrive - Middlebury College\\Last Semester\\ECON Inequality & Justice\\econ0401\\white_combined.png",
                              "C:\\Users\\neris\\OneDrive - Middlebury College\\Last Semester\\ECON Inequality & Justice\\econ0401\\kfr_combined.png",
                              "C:\\Users\\neris\\OneDrive - Middlebury College\\Last Semester\\ECON Inequality & Justice\\econ0401\\top20_combined.png"),
                     text = c("The table presents estimates of the effect of the number of colleges, four year, or public colleges on the mean predicted income rank of Black children with parent income percentile as defined by the column headers. Controls are population density and median household income. The results suggest that having any college or a public college nearby has a slightly negative effect for children from below the median but has less effect on children from above the median, and four year colleges have no significant effect at all. Although statistically significant, the largest coefficient is the effect of number of public colleges on the top 1%, which is -0.0041, or 2.7% of a standard deviation, which is rather small.",
                              "The table presents estimates of the effect of the number of colleges, four year, or public colleges on the mean predicted income rank of white children with parent income percentile as defined by the column headers. Controls are population density and median household income. The results suggest that having any college or a four year college nearby have little to no effect on income rank, and but that public colleges may have a slightly negative effect for those at the 75th percentile and below. Although statistically significant, the largest coefficient is the effect of number of public colleges on the bottom 1%, which is -0.0053, or 7.7% of a standard deviation, which is rather small. ",
                              "The table presents estimates of the effect of the number of colleges, four year, or public colleges on the mean predicted income rank of children with parent income percentile as defined by the column headers. Controls are population density and median household income. The results suggest that having a college nearby has a slightly negative effect for children from below the median but has less effect on children from above the median. Although statistically significant, the largest coefficient is the effect of number of public colleges on the bottom 1%, which is -0.0068, or 9.3% of a standard deviation, which is rather small. This means that with an increase of one public school, the mean percentile rank is predicted to decrease by 0.68 percentage points.",
                              "The table presents estimates of the effect of the number of colleges, four year, or public colleges on the mean predicted probability that a child with parents from a given income percentile reaches the top income quintile. Controls are population density and median household income.  The results suggest that having a college nearby has a slightly negative effect for children from below the median but has less effect on children from above the median, with number of public colleges having the greatest effect. Although statistically significant, the largest coefficient is the effect of number of public colleges on the bottom 1%, which is -0.0039, or only 7.3% of a standard deviation."))

# write_csv(outputtables, "regouttables.csv")

```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
